Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-08 aggregation/agg-multioutput.tex
Late nite work

In the disclosure framework, any manner of production-balanced partitioning can be represented by including the raw, un-allocated inventory as one foreground column, choosing any output as the reference.  The other $n-1$ outputs are then included as arbitrarily-specified allocated inventories in additional columns, for a total of $n$ columns.  Each column must be normalized to a unit reference.  The reference flow not explicitly specified will simply be computed as the remainder when the allocated inventories are subtracted from the un-allocated inventory.

@@

At the same time, LCA computation using a functional unit of one of the co-products will simply make use of the allocated inventory.  In this example, all processes are identical on a mass basis, but any other partitioning allocation can be automatically rendered self-consistent through this approach.  A reviewer would be able to inspect the foreground model to determine whether the allocation was performed as described in the report.

@@

Although the term `system expansion' is often used to refer to product substitution and/or alternate activity allocation, these modeling techniques are distinct and should be referred to with different names, as noted in GWS14.  In the original definition of system expansion, the foreground model is simply enlarged to include all co-products.  Representation of such a system is trivial and is shown in Table~\ref{tbl:cse}.

@@

In the classical system expansion case, the canonical functional unit, production of 1 kg of chlorine gas, will result in two cutoff flows corresponding to outputs of liquid hydrogen and sodium hydroxide.  Equivalently, an expanded functional unit of 1 kg chlorine, plus 0.028 kg hydrogen and 1.13 kg of sodium hydroxide, will result in the same activity of the un-allocated process, but will generate no cutoff flows at net.

@@

Here an alternate activity, namely electrolysis of water, is specified for liquid hydrogen production and is specified at index 3 in the foreground  (shown in blue).  The inventory converts 9 kg of water to 1 kg of hydrogen using 50 kWh of electricity.  The hydrogen produced from the multi-output process is then (somewhat dubiously) taken to displace hydrogen produced through the alternate activity by introducing a unity coefficient in row 3, column 1 of $A_f$.

Meanwhile, sodium hydroxide from the process is assumed to substitute the production of magnesium hydroxide through the introduction of a new row and a new nonzero coefficient in column 2 of $A_d$ (shown in red). Here the match is inexact, and because magnesium hydroxide is more effective in some applications, 1 kg of sodium hydroxide is taken to displace only 0.8 kg of magnesium hydroxide.

>>>>

In the disclosure framework, any manner of production-balanced partitioning can be represented by including the raw, un-allocated inventory as one foreground column, choosing any output as the reference.  The other $n-1$ outputs are then included as arbitrarily-specified allocated inventories in additional columns, for a total of $n$ columns.  Each column must be normalized to a unit reference.  The reference flow not explicitly allocated will simply be computed as the remainder when the allocated inventories are subtracted from the un-allocated inventory.

@@

At the same time, LCA computation using a functional unit of one of the co-products will simply make use of the allocated inventory.  In this example, all processes are identical on a mass basis, but any other partitioning allocation can also be automatically rendered self-consistent through this approach.  A reviewer would be able to inspect the foreground model to determine whether the allocation was performed as described in the report.

@@

Although the term `system expansion' is often used to refer to product substitution and/or alternate activity allocation, these modeling techniques are distinct and should be referred to with different names, as noted in GWS14.  In the original definition of system expansion, the functional unit is simply enlarged to include all co-products.  Representation of such a system is trivial and is shown in Table~\ref{tbl:cse}.

@@

In the classical system expansion case, applying the expanded functional unit of 1 kg chlorine, plus 0.028 kg hydrogen and 1.13 kg of sodium hydroxide, will result in a unit activity of the reference process, without any cut-off flows..  Equivalently, the canonical functional unit, production of 1 kg of chlorine gas, will result in the same process activity level, and will also generate the co-products as cutoff flows.

@@

Here an alternate activity, namely electrolysis of water, is included for liquid hydrogen production and is specified at index 3 in the foreground  (shown in blue).  The inventory converts 9 kg of water to 1 kg of hydrogen using 50 kWh of electricity.  The hydrogen produced from the multi-output reference process is (somewhat dubiously) taken to displace hydrogen produced through the alternate activity by introducing a unity coefficient in row 3, column 1 of $A_f$.

Meanwhile, sodium hydroxide from the reference process is modeled to substitute the production of magnesium hydroxide through the introduction of a new row and a new nonzero coefficient in column 2 of $A_d$ (shown in red). Here the match is inexact, and because magnesium hydroxide is more effective in some applications, 1 kg of sodium hydroxide is taken to displace only 0.8 kg of magnesium hydroxide.

### 2018-02-08 aggregation/agg-requirements.tex
Multioutput case in SI
Late nite work

\subsection{Meeting the Disclosure Objectives}

\subsubsection{Transparency}

@@

The foreground nodes, which make up the columns of $A_f$, can be chosen freely by the study author according to the objectives of the study.  Large studies may contain hundreds of foreground nodes, and the nodes can correspond to physical activities, logical operations, unit conversions, accumulation or distribution points, or any other aspect of model construction that can be reflected in a process-flow diagram.  The only requirement on their disclosure is that the identity of each node's reference flow, including its unit of measure, is clearly stated.  In formalizing the study as a normalized direct requirements matrix, the activity level of each foreground node necessarily equals the magnitude of the total reference flow emanating from the node.

For each row in $A_d$ containing a non-zero entry, the author must unambiguously identify the exact dataset used, including the version of the database, as well as the exact process and reference flow selected; the dimension (reference quantity or unit) of each reference flow must be specified; and the sign of the numeric entry in $A_d$ must be consistent with the implementation of the process in the background database.  Similarly, for each row in $B_f$ containing a non-zero entry, the author must unambiguously identify the substance being exchanged with the environment, the compartment or context into which it is being exchanged, and the reference quantity or unit associated with the flow.  Sign consistency must also be assured.  If LCIA indicator results are included, the author must also unambiguously identify the method computed (identity of $\mathbf{e}$).

\subsubsection{Authority and Primacy}

>>>>

\section{Meeting the Disclosure Objectives}

\subsection{Transparency}

@@

The foreground nodes, which make up the columns of $A_f$, can be chosen freely by the study author according to the objectives of the study.  Large studies may contain hundreds of foreground nodes, and the nodes can correspond to physical activities, logical operations, unit conversions, accumulation or distribution points, or any other aspect of model construction that can be reflected in a process-flow diagram.  The only requirement on their disclosure is that the identity of each node's reference flow, including its unit of measure, is clearly stated.

For each row in $A_d$ containing a non-zero entry, the author must unambiguously identify the exact dataset used, including the version of the database, as well as the exact process and reference flow selected; the dimension (reference quantity or unit) of each reference flow must be specified; and the sign of the numeric entry in $A_d$ must be consistent with the implementation of the process in the background database.  Similarly, for each row in $B_f$ containing a non-zero entry, the author must unambiguously identify the substance being exchanged with the environment, the compartment or context into which it is being exchanged, and the reference quantity or unit associated with the flow.  Sign consistency must also be assured.  If LCIA indicator results are included, the author must also unambiguously identify the method computed (identity of $\mathbf{c}$).

\subsection{Authority and Primacy}
